---
title: "Textual Sentiment Analysis"
author: "Mandip Mistry"
date: "07/08/2020"
output: html_document
---

Learning outcomes

As part of this tutorial, you will learn how to:

- Decompose your texts into bins (typically equal-sized containers of words) or sentences.
 -Compute sentiment with a variety of weighting schemes.
 -Create and use your own weighting scheme for a classification task.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("data.table")    # package bringing in the data.table machinery
library("quanteda")      # package useful for text and corpus manipulation
library("sentometrics")  # package containing sentiment computation tools
library("lexicon")       # package with multiple lexicons
library(dpl)

# Bring in Data on UVXY
vol_news <- do.call(rbind, lapply(c("TSLA"), get_all_news, 90))
# Use the description as the text data set
news_from_source <- vol_news %>%
    select(id, publishedDate, description) %>%
    rename(date = publishedDate, texts = description) %>% 
  distinct()
    
news_sento <- sentometrics::sento_corpus(news_from_source)

# Create 2 Lexicons 1 Base one on Absolute values
lex <- lexicon::hash_sentiment_jockers_rinker

sentoLexicon <- sento_lexicons(list(baseLex = lex,
                                    absoluteLex = lex[, .(x = x, y = abs(y))]))
lapply(sentoLexicon, head)

#

```

A review of sentiment computation with sentometrics

When using the default settings (i.e., only specifying the how argument), the sentiment for each word within a text will be determined according to the provided lexicons. This word-level sentiment is then aggregated using the method defined by the how argument, aggregating up to the document level to form a sentiment value for the document.

```{r}
sentiment_by_word <- compute_sentiment(news_sento, sentoLexicon, how = "proportional")
head(sentiment_by_word)

sentiment_by_sentence <- sentiment <- compute_sentiment(news_sento, sentoLexicon, how = "proportional", do.sentence = TRUE)
head(sentiment_by_sentence)
```

Plot what you got

You could bin by date every 5 days or something 

```{r}
par(mfrow = c(1, 2))

plot(sentiment_by_word[, .(s = mean(`absoluteLex--dummyFeature`)), by = date], type = "l",
     ylab = "Mean absolute sentiment")

boxplot(sentiment_by_sentence$`absoluteLex--dummyFeature` ~ sentiment_by_sentence$date, ylab = "Absolute sentiment",
        xlab = "Bin", outline = FALSE, range = 0.5)

```

